LaTeX draft for \\"Ancient Greece Yuri Visual Novel"

### 2015-09-09 text/draft.tex
First try at actually wirting a conversation

@@

@@

>>>>

\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks,
    linkcolor=blue,
}

@@

\newcommand{\speaker}[1]{
	\textbf{#1}: 
}

@@

\chapter*{A talk}

\section*{Alone in the crowd}

I advance quickly through the many rooms of the building, getting around and stepping over the many revelers crossing my path with a consummate skill. I have worked at many similar parties before, and experience taught me how to move with ease despite the chaotic crowd.\\

I make a breach through human walls with a smile and a gentle but firm arm, adroitly avoid stepping on discarded leftovers and other unsavory things, nicely dismiss people asking for a song.\\

While my reflexes alone handle my movements and keep my pace, I gaze at every single person, my sight jumping from face to face, hunting the only prey worth it. A hundred different eyes meet mine, but not the ones I desire. Until they finally lock into perfection.\\

They may right now display the slight luster symptomatic of an important consumption of alcohol. But they still shine like twin suns. The reflected flames of the candles dance upon the dark and brown ocean, shifting with the emotions of their owner. Enlarged from the surprise of the sudden encounter. Contracted as she observes the intruder. Sparkling when she recognizes me.\\

She instantly drops off her plate of food, rises from her makeshift seat, and jumps to hug me. Her warm arms vigorously lock behind my back in a frank embrace, bringing my face mere centimeters of her own.\\

\dcomment{
	A simple zoom in on the sprite should do the job. Cheap, but efficient.
}

This is a purely friendly greeting, yet it takes all my will to keep my heartbeat in check. After an ephemeral eternity, Antiope releases me and speaks.\\

\speaker{Antiope} "Ambrosia! Where have you been? You just disappeared after your performance at the poetry contest. I was unable to find you anywhere. That's so unlike you!"\\

I smile timidly. It's true that I sneaked out as soon as my obligations were fulfilled, walking away for a long time, only returning at dusk. But I did so to have some time alone, to calm down myself after the frenzy of the morning, to think about the future of both of us at peace.

\begin{itemize}
	\item \hyperref[A1]{Reveal that I needed the solitude}
	\item \hyperref[A2]{Avoid the subject and praise her for her own achievement}
\end{itemize}

\section*{We need to talk}

\label{A1}

\speaker{Ambrosia} "I needed a break. To put some distance between me and the crowd. To think."\\

I barely recognize my own voice. It sounds so... depressed. Antiope blinks, and grabs my hand, her face suddenly serious, concerned.\\

\speaker{Antiope} "Ambrosia, are you alright? Is there something wrong? You're not acting like yourself. Are you sick? Had someone done something to you?"\\

Yes dummy, someone has. That someone is you.

\begin{itemize}
	\item \hyperref[A3]{Reassure her}
	\item \hyperref[A4]{Ask if we can discuss somewhere else}
\end{itemize}

\section*{Praise the beauty of the body}

\label{A2}

\section*{Everything's alright}

\label{A3}

\section*{The garden}

\label{A4}

\speaker{Ambrosia} "Can we talk about this in a calmer and quieter place?"\\

This statement does not reassure Antiope a bit. She looks around, appears to notice the many people around us, even if most actually pay no attention to our little show, busy that they are with their friends or drinks, but still contributing to the stifling atmosphere of the overfull room.\\

She then reacts with her natural straightforwardness. Grabbing you by the wrist, she walks right through the crowd, taking the shortest route to the nearest exit. If you got here like a breeze, slipping in cracks and leaving no trace of your passing behind you, Antiope is a ram, a spur, elbowing her way out, breaking any resistance like a charging bull.\\

I should probably scold her for her rude behavior. But I cannot resolve myself to do it. Partly because I realize I really want to go out. Partly because I'm somehow happy, even if this happiness is tainted with guilt, that she is worried about me, that did not hesitate for one second to discard all decorum for me.
